---
title: "Scripts"
author: "Hendrik van Broekhuizen"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 8
    fig_height: 4
    dev: svg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center', dev = 'svg', fig.width = 8, fig.height = 4)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
# load libaries
library(tidyverse)


# function to extract metadata from scripts
my.metadata <- function(filename, caption = '') {
  metadata <- data.frame(line = readLines(filename)) %>% 
  mutate(group = ifelse(line == '' & lag(line) != '', 1, 0) %>% cumsum()) %>% 
  filter(grepl('^# ', line) & group %in% c(0, 1)) %>% 
  mutate(line = line %>% 
           gsub('^# ', '', .) %>% 
           gsub('^METADATA.*$', '', .)) %>%
  filter(line != '') %>% 
  separate(line, into = c('header', 'string'), sep = ': ', fill = 'left') %>% 
  mutate(header = header %>% stringr::str_to_title()) %>% 
  group_by(group) %>% 
  mutate(string = ifelse(group == 1, paste0(string, collapse = ' '), string)) %>% 
  ungroup() %>% 
  filter(header != '') %>% 
  mutate(printstring = paste0('- **', header, ':** ', string)) %>% 
  select(printstring) 
  
  if (caption != '') {
    metadata <- metadata %>% 
      add_row(printstring = paste(caption, '\n'), .before = 1)
  }
  
  metadata  %>% 
    add_row(printstring = '\n') %>% 
    .[[1]] %>%
    cat(fill = T)
}


```

Users can create the processed version of the _QLFS panel data_ contained in `data/processed/qlfs_panel.RDS` by executing the `.R` scripts in this folder in the following order^[Note that `data/processed/qlfs_panel.RDS` contains only a subset of the variables from the _QLFS_ data.  Users wishing to expand/alter this subset will need to edit the `scripts/process_qlfs_panel.R` script.]: 

```{r echo=F, message=FALSE, warning=FALSE, results='asis'}
my.metadata('scripts/create_qlfs_pooled.R', '### 1.`create_qlfs_pooled.R`')
my.metadata('scripts/create_lmd_pooled.R', '### 2.`create_lmd_pooled.R`')
my.metadata('scripts/create_cpi.R', '### 3.`create_cpi.R`')
my.metadata('scripts/create_qlfs_panel.R', '### 4.`create_qlfs_panel.R`')
my.metadata('scripts/process_qlfs_panel.R', '### 5.`process_qlfs_panel.R`')
```

